\begin{mydefn}
Suppose $A$ is a finitely generated augmented graded $k$-algebra, then $A$ is called a $d$-dimensional Artin-Shelter regular algebra if 
\begin{itemize}
    \item $\gldim (A) =d $
    \item $\gkdim (A) < \infty$
    \item as left $A$-modules, if $i \neq d$,then $\underline{\ext}_{A}^{i}(k,A)=0 $, otherwise $\underline{\ext}_{A}^{i}(k,A)=s^{l}k$ for some $l \in \mathbb{Z}$
\end{itemize}
\end{mydefn}
In this paper, we will abbreviate Artin-Shelter regular algebra to AS regular algebra.\\
\begin{ex}[quantum plane]
Let $q \neq 0 \in k $ is a constant
\[
A= k\langle{x,y}\rangle /(yx - qxy)
\]
This quadratic algebra is called quantum plane, and it is a basic notion in noncommutative geometry. In this case, $V= k^{2}$ and $R=(yx-qxy)$ so $R^{\bot}=((x^{*})^2,(y^{*})^2,x^{*}y^{*}+q^{-1}y^{*}x^{*})$. Hence Koszul dual algebra is 
\[
{A}^{!} \simeq k \langle{sx',sy'}\rangle /(sx' \otimes sx', sy' \otimes sy', sx' \otimes sy' + q^{-1} sy' \otimes sx')
\]
Then 
\begin{align*}
    ({A}^{!})^{(n\geq 3)}=0 &  &
    ({A}^{!})^{(2)} \simeq ks(x' \otimes y')& &
    ({A}^{!})^{(1)} \simeq ksx' \oplus ksy' \\
    (\kdual{A})^{(n\geq 3)}=0 &  &
    (\kdual{A})^{(2)} \simeq ks(yx-qxy)& &
    (\kdual{A})^{(1)} \simeq ksx \oplus ksy 
\end{align*}
So the Koszul complex $A \otimes_{k} \kdual{A}$ can be written as 
\[
0 \rightarrow s^{2}A(yx-qxy) \xlongrightarrow{(-q^{-1}y,x)} sA(x) \oplus sA(y) \xlongrightarrow{
\bigl(\begin{smallmatrix}
x\\
y
\end{smallmatrix} \bigr) }A \rightarrow 0 
\]
It's simple to check it is acyclic, that is,  $A$ is Koszul algebra. So it is the minimal free resolution of $A$, so $\gldim(A)=2$. Apply Hom functor $\text{Hom}_{A}(-,A)$ on the chain complex, then it is canonical isomorphic to
\[
0 \leftarrow A \xlongleftarrow{(-q^{-1}y,x)} sA \oplus sA \xlongleftarrow{
\bigl(\begin{smallmatrix}
x\\
y
\end{smallmatrix} \bigr) }s^{2}A \leftarrow 0 
\]
Compute this homology, we get  $\underline{\ext}_{A}^{i}(k,A)=0$ except $\underline{\ext}_{A}^{2}(k,A)=k$. Hence it is AS regular algebra.
\end{ex}
\begin{ex}[Jordan plane]
\[
A=k\langle{x,y}\rangle /(yx-xy-x^{2})
\]
Jordan plane can be viewed as a quadratic algebra related to quadratic data $(V,R)$ where $V=kx \oplus ky$ and $R=(yx - xy -x^{2})$. $R^{\bot}$ is generated by three element $(y^{*})^{2}$, $x^{*}y^{*}+y^{*}x^{*}$ and $(x^{*})^{2} + y^{*} x^{*}$.So
\[
{A}^{!} \simeq k \langle{sx',sy'}\rangle /(sy' \otimes sy', sx' \otimes sy'+ sy' \otimes sx', sx' \otimes sx' + sy' \otimes sx')
\]
Then 
\begin{align*}
    ({A}^{!})^{(n\geq 3)}=0 &  &
    ({A}^{!})^{(2)} \simeq ks(x' \wedge y')& &
    ({A}^{!})^{(1)} \simeq ksx' \oplus ksy' \\
    (\kdual{A})^{(n\geq 3)}=0 &  &
    (\kdual{A})^{(2)} \simeq ks(yx-xy-x^{2})& &
    (\kdual{A})^{(1)} \simeq ksx \oplus ksy 
\end{align*}
Koszul complex $A \otimes_{k} \kdual{A}$
\[
0 \rightarrow s^{2}A(yx-xy-x^{2}) \xlongrightarrow{(y-x,x)} sA(x) \oplus sA(y) \xlongrightarrow{
\bigl(\begin{smallmatrix}
x\\
y
\end{smallmatrix} \bigr) }A \rightarrow 0 
\]
Exactly, it's same as discussion in case of quantum plane, Jordan plane is Koszul and also AS regular.
\end{ex}
From this example, we can see that if a quadratic algebra is Koszul, then it may be easier to check if it is also AS regular since its left Koszul complex is a minimal resolution of $A$. Unfortunately, there exists algebra that is AS regular but not Koszul. For instance,
\begin{ex}
Let
\[
A = k\langle{x,y}\rangle /(yx^{2}-x^{2}y, y^{2}x -xy^{2})
\]
Its minimal free resolution of $k$ is 
\[
0 \rightarrow s^{4}A \xlongrightarrow{
(y,-x)} s^{3}A \oplus s^{3}A \xlongrightarrow{
\bigl(
\begin{smallmatrix}
-xy & x^{2}\\
-y^2 & yx
\end{smallmatrix}
\bigr)}sA \oplus sA\xlongrightarrow{
\bigl(\begin{smallmatrix}
x\\
y
\end{smallmatrix}
\bigr)} A \rightarrow 0
\]
By the resolution, $A$ can be proved to be 3-dimensinal AS regular algebra, see[ref] for details. \\
While the Hilbert series of $A$ is $h_{A}(t)=1/(1-t)^{2}(1-t^{2})$, so $1/h_{A}(-t)=(1+t)^{2}(1-t^{2})$ has negative terms thus it is not a Koszul algebra.  
\end{ex}
In dimension 2, we have a good classification of regular algebra
\begin{thm}
Suppose $A$ is a finitely generated graded algebra which is generated in degree 1 that $\gldim(A)=2$. If $A$ is AS regular algebra, then $A$ is isomorphic to quantum plane or Jordan plane.
\end{thm}
Proof of the theorem can be seen in \cite[ref][]{Roga2014}.
\begin{cor}
Any 2-dimensional AS regular algebra is Koszul algebra.
\end{cor}
\begin{proof}
Since it is already known quantum plane and Jordan plane are both Koszul algebra, we can conclude that any AS regular algebra in dimension 2 is Koszul algebra. 
\end{proof}
